### 2022-03-14 paper/output/document/thesis_4_applications.tex
CLEANING DONE

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}applications}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Applications \label{applications}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this chapter, I demonstrate that my system can produce correct judgements for challenging moral 
dilemmas that naive ethical reasoning cannot satisfactorily handle. Because my system is faithful to
philosophical literature, it can reproduce complex ethical judgements presented by philosophers as 
solutions to controversial open questions in ethics.
These dilemmas serve as examples of how my system could be used
in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
than those presented in Chapter \ref{details}.

@@

There are two implications of this section. First, my system is capable of performing ethical reasoning
sophisticated enough to show that lying is prohibited but joking is not. This is a direct consequence 
of my system's use of a robust conception of a maxim, which encodes the goal of an act as part of the 
maxim being evaluated. Because my implementation is faithful to philosophical literature, it is able 
to recreate Korsgaard's solution to a complex ethical dilemma that philosophers debated for decades. Second, 
in the process of making this argument precise, my system isolated a necessary and sufficient condition 
of a maxim about uttering a falsehood being prohibited: that the goal require that someone believe
the falsehood. This condition both made an long-standing argument in Kantian ethics more precise
and can guide the correct formulation of future maxims. In other words, an insight generated by the 
computer provides value to ethicists, bolstering the argument for computational ethics provided in 
Section \ref{computationalethics}.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Lying to a Liar \label{murderer}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
My system can not only distinguish between lying and joking, but it can also resolve the paradox of 
the murderer at the door. In this dilemma, murderer Bill knocks on your door asking about Sara, his 
intended victim. Sara is at home, but moral intuition says that you should lie to Bill and say 
that she is out to prevent him from murdering her. Many critics of Kantian ethics argue that the 
FUL prohibits you from lying in this instance; if everyone lied to murderers, then murderers wouldn't 
believe the lies and would search the house anyways. Korsgaard resolved this centuries-long debate by 
noting that the maxim of lying to a murderer is actually that of lying to a liar: Bill cannot 
announce his intentions to murder; instead, he must ``must suppose that you do not know who he is 
and what he has in mind'' \citep{KorsgaardRTL}.\footnote{Korsgaard assumes that the murderer will 
lie about his identity in order to take advantage of your honesty to find his victim. In footnote 5, 
she accepts that her arguments will not apply in the case of the honest murderer 
who announces his intentions, so she restricts her focus to the case of lying to a liar. She claims 
that in the case of the honest murderer, the correct act is to refuse to respond. Since I am formalizing
Korsgaard's argument, I also accept this assumption.} Thus, the maxim 
in question specifies that when someone lies to you, you are allowed to lie to them. The maxim of 
lying to the murderer is actually the maxim of lying to a liar, which is permissible.

@@

%:%92=58%:%
%:%104=61%:%
%:%105=62%:%

@@

%:%127=85%:%
%:%128=85%:%
%:%130=86%:%
%:%131=87%:%

@@

%:%135=90%:%
%:%136=91%:%

@@

%:%143=99%:%
%:%144=99%:%
%:%146=100%:%
%:%147=101%:%
%:%148=101%:%
%:%149=102%:%
%:%150=102%:%
%:%151=103%:%
%:%153=104%:%
%:%154=104%:%
%:%155=105%:%
%:%156=105%:%
%:%157=106%:%
%:%159=107%:%
%:%160=108%:%

@@

%:%166=115%:%
%:%167=116%:%

@@

@@

%:%178=126%:%
%:%179=127%:%
%:%181=128%:%
%:%184=130%:%
%:%185=131%:%

@@

@@

%:%199=144%:%
%:%201=145%:%
%:%202=146%:%

@@

%:%204=147%:%
%:%205=148%:%
%:%206=148%:%
%:%208=149%:%
%:%209=150%:%
%:%210=150%:%
%:%211=151%:%
%:%212=151%:%
%:%214=152%:%
%:%217=154%:%
%:%218=155%:%

@@

@@

%:%223=159%:%
%:%224=160%:%

@@

%:%227=162%:%
%:%228=162%:%
%:%229=163%:%
%:%231=164%:%
%:%232=165%:%
%:%233=165%:%
%:%234=166%:%
%:%236=167%:%
%:%237=168%:%

@@

%:%242=172%:%
%:%243=173%:%
%:%245=174%:%
%:%246=174%:%
%:%247=175%:%
%:%254=176%:%
%:%255=176%:%
%:%256=177%:%
%:%257=177%:%
%:%258=178%:%
%:%259=178%:%
%:%261=179%:%
%:%262=180%:%

@@

%:%265=182%:%
%:%266=183%:%
%:%267=183%:%
%:%268=184%:%
%:%269=184%:%
%:%270=185%:%
%:%271=185%:%
%:%272=186%:%
%:%273=186%:%
%:%274=186%:%
%:%276=187%:%
%:%277=188%:%
%:%278=188%:%
%:%279=189%:%
%:%289=191%:%
%:%290=192%:%

@@

@@

%:%306=207%:%
%:%307=208%:%
%:%309=209%:%
%:%310=210%:%
%:%313=212%:%
%:%314=213%:%

@@

@@

%:%324=222%:%
%:%325=223%:%

@@

%:%328=225%:%
%:%329=225%:%
%:%330=226%:%
%:%332=227%:%
%:%333=228%:%
%:%334=228%:%
%:%335=229%:%
%:%337=230%:%
%:%338=230%:%
%:%339=231%:%
%:%341=232%:%
%:%342=232%:%
%:%343=233%:%
%:%346=234%:%
%:%350=234%:%
%:%351=234%:%
%:%353=235%:%
%:%354=236%:%

@@

%:%367=242%:%
%:%368=243%:%

@@

%:%420=289%:%
%:%432=292%:%
%:%433=293%:%
%:%434=294%:%

@@

@@

%:%453=312%:%
%:%455=313%:%
%:%456=313%:%
%:%457=314%:%
%:%458=314%:%
%:%460=315%:%
%:%461=316%:%
%:%462=317%:%
%:%463=317%:%
%:%464=318%:%
%:%465=318%:%
%:%467=319%:%
%:%468=319%:%
%:%469=320%:%
%:%470=320%:%
%:%472=321%:%
%:%473=321%:%
%:%474=322%:%
%:%475=322%:%
%:%476=323%:%
%:%478=324%:%
%:%479=325%:%
%:%482=327%:%
%:%483=328%:%
%:%484=329%:%

@@

@@

%:%488=332%:%
%:%490=333%:%
%:%491=333%:%
%:%492=334%:%
%:%493=334%:%
%:%494=335%:%
%:%496=336%:%
%:%497=336%:%
%:%498=337%:%
%:%499=337%:%
%:%501=338%:%
%:%502=338%:%
%:%503=339%:%
%:%504=339%:%
%:%505=340%:%
%:%507=341%:%
%:%508=342%:%
%:%524=374%:%
%:%525=375%:%
%:%526=376%:%

@@

@@

%:%535=384%:%
%:%536=385%:%
%:%537=386%:%
%:%539=387%:%
%:%540=387%:%
%:%541=388%:%
%:%543=389%:%
%:%544=389%:%
%:%545=390%:%
%:%547=391%:%
%:%548=392%:%
%:%549=393%:%

@@

%:%552=395%:%
%:%553=396%:%
%:%555=397%:%
%:%556=398%:%
%:%557=399%:%

@@

%:%562=403%:%
%:%563=404%:%
%:%565=405%:%
%:%566=406%:%
%:%567=406%:%
%:%568=407%:%
%:%571=408%:%
%:%575=408%:%
%:%576=408%:%
%:%577=408%:%
%:%579=409%:%
%:%580=410%:%
%:%581=411%:%
%:%591=413%:%
%:%592=414%:%
%:%593=415%:%

@@

@@

%:%597=418%:%
%:%598=419%:%
%:%600=420%:%
%:%601=420%:%
%:%602=421%:%
%:%604=422%:%
%:%605=422%:%
%:%606=423%:%
%:%608=424%:%
%:%609=424%:%
%:%610=425%:%
%:%612=426%:%
%:%613=426%:%
%:%614=427%:%
%:%616=428%:%
%:%617=429%:%
%:%618=429%:%
%:%619=430%:%
%:%626=431%:%
%:%627=431%:%
%:%628=432%:%
%:%629=432%:%
%:%630=433%:%
%:%631=433%:%
%:%632=433%:%
%:%633=434%:%
%:%634=434%:%
%:%635=435%:%
%:%636=435%:%
%:%637=435%:%
%:%638=436%:%
%:%639=436%:%
%:%640=437%:%
%:%641=437%:%
%:%642=437%:%
%:%643=438%:%
%:%653=440%:%
%:%654=441%:%
%:%655=442%:%

@@

>>>>

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}applications}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Applications \label{applications}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this chapter, I demonstrate that my system can produce correct judgements for challenging moral 
dilemmas that naive ethical reasoning cannot satisfactorily handle. Because my system is faithful to
philosophical literature, it can reproduce complex ethical judgements presented by philosophers as 
solutions to controversial open questions in ethics.
These dilemmas serve as examples of how my system could be used
in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
than those presented in Chapter \ref{details}. Moreover, in the process of formalizing these dilemmas, 
I isolated the exact conditon that makes a maxim about lying wrong, an insight that could contribute to 
the philosophical literature on lying.

@@

There are two implications of this section. First, my system is capable of performing ethical reasoning
sophisticated enough to show that lying is prohibited but joking is not. This is a direct consequence 
of my system's use of a robust conception of a maxim, which encodes the goal of an act as part of the 
maxim being evaluated. Because my implementation is faithful to philosophical literature, it is able 
to recreate Korsgaard's solution to a complex ethical dilemma that philosophers debated for decades. Second, 
in the process of making this argument precise, my system isolated a necessary and sufficient condition 
of a maxim about uttering a falsehood being prohibited: that the goal require that someone believe
the falsehood. This condition, made an long-standing argument in Kantian ethics more precise, can guide 
the correct formulation of future maxims, and could contribute to the rich philosophical conversation
about the wrongness of lying. In other words, an insight generated by the
computer provides value to ethicists, bolstering the argument for computational ethics provided in 
Section \ref{computationalethics}.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Lying to a Liar \label{murderer}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
My system can not only distinguish between lying and joking, but it can also resolve the paradox of 
the murderer at the door. In this dilemma, murderer Bill knocks on your door asking about Sara, his 
intended victim. Sara is at home, but moral intuition says that you should lie to Bill and say 
that she is out to prevent him from murdering her. Many critics of Kantian ethics argue that the 
FUL prohibits you from lying in this instance; if everyone lied to murderers, then murderers wouldn't 
believe the lies and would search the house anyways. Korsgaard resolved this centuries-long debate by 
noting that the maxim of lying to a murderer is actually that of lying to a liar: Bill cannot 
announce his intentions to murder; instead, he must ``must suppose that you do not know who he is 
and what he has in mind'' \citep{KorsgaardRTL}.\footnote{Korsgaard assumes that the murderer will 
lie about his identity in order to take advantage of your honesty to find his victim. In footnote 5, 
she accepts that her arguments will not apply in the case of the honest murderer 
who announces his intentions, so she restricts her focus to the case of lying to a liar. She claims 
that in the case of the honest murderer, the correct act is to refuse to respond. Since I am formalizing
Korsgaard's argument, I also accept this assumption.} Thus, the maxim 
in question specifies that when someone lies to you, you are allowed to lie to them. The maxim of 
lying to the murderer is actually the maxim of lying to a liar, which is permissible.

@@

%:%84=56%:%
%:%85=57%:%
%:%94=60%:%

@@

%:%126=83%:%
%:%127=84%:%
%:%129=87%:%
%:%130=87%:%

@@

%:%133=89%:%
%:%134=90%:%

@@

%:%142=97%:%
%:%143=98%:%
%:%145=101%:%
%:%146=101%:%
%:%148=102%:%
%:%149=103%:%
%:%150=103%:%
%:%151=104%:%
%:%152=104%:%
%:%153=105%:%
%:%155=106%:%
%:%156=106%:%
%:%157=107%:%
%:%158=107%:%
%:%159=108%:%

@@

%:%164=112%:%
%:%165=113%:%

@@

%:%176=125%:%

@@

%:%179=128%:%
%:%180=128%:%
%:%181=129%:%
%:%183=130%:%

@@

%:%197=143%:%

@@

%:%200=146%:%
%:%201=146%:%

@@

%:%204=148%:%
%:%205=149%:%
%:%206=149%:%
%:%207=150%:%
%:%208=150%:%
%:%210=151%:%
%:%211=152%:%
%:%212=152%:%
%:%213=153%:%
%:%214=153%:%
%:%216=154%:%

@@

%:%221=158%:%

@@

%:%224=161%:%

@@

%:%226=162%:%
%:%227=163%:%
%:%229=164%:%
%:%230=164%:%
%:%231=165%:%
%:%233=166%:%
%:%234=167%:%
%:%235=167%:%
%:%236=168%:%

@@

%:%242=173%:%
%:%243=174%:%
%:%244=174%:%
%:%245=175%:%
%:%247=176%:%
%:%248=176%:%
%:%249=177%:%
%:%256=178%:%
%:%257=178%:%
%:%258=179%:%
%:%259=179%:%
%:%260=180%:%
%:%261=180%:%

@@

%:%265=183%:%
%:%266=184%:%
%:%267=184%:%
%:%268=185%:%
%:%269=185%:%
%:%270=186%:%
%:%271=186%:%
%:%272=187%:%
%:%273=187%:%
%:%274=188%:%
%:%275=188%:%
%:%276=188%:%
%:%278=189%:%
%:%279=190%:%
%:%280=190%:%
%:%281=191%:%

@@

%:%304=206%:%

@@

%:%307=209%:%
%:%308=209%:%
%:%309=210%:%
%:%311=211%:%
%:%312=212%:%

@@

%:%322=221%:%

@@

%:%325=224%:%

@@

%:%327=225%:%
%:%328=226%:%
%:%330=227%:%
%:%331=227%:%
%:%332=228%:%
%:%334=229%:%
%:%335=230%:%
%:%336=230%:%
%:%337=231%:%
%:%339=232%:%
%:%340=232%:%
%:%341=233%:%
%:%343=234%:%
%:%344=234%:%
%:%345=235%:%
%:%348=236%:%
%:%352=236%:%
%:%353=236%:%

@@

%:%358=240%:%
%:%359=241%:%

@@

%:%412=287%:%
%:%413=288%:%
%:%414=289%:%
%:%423=292%:%

@@

%:%451=311%:%

@@

%:%453=313%:%
%:%455=315%:%
%:%456=315%:%
%:%458=316%:%
%:%459=316%:%
%:%460=317%:%
%:%461=317%:%
%:%463=318%:%
%:%464=319%:%
%:%465=320%:%
%:%466=320%:%
%:%467=321%:%
%:%468=321%:%
%:%470=322%:%
%:%471=322%:%
%:%472=323%:%
%:%473=323%:%
%:%475=324%:%
%:%476=324%:%
%:%477=325%:%
%:%478=325%:%
%:%479=326%:%
%:%481=327%:%
%:%482=328%:%

@@

%:%486=331%:%

@@

%:%488=333%:%
%:%490=335%:%
%:%491=335%:%
%:%493=336%:%
%:%494=336%:%
%:%495=337%:%
%:%496=337%:%
%:%497=338%:%
%:%499=339%:%
%:%500=339%:%
%:%501=340%:%
%:%502=340%:%
%:%504=341%:%
%:%505=341%:%
%:%506=342%:%
%:%507=342%:%
%:%508=343%:%
%:%510=344%:%
%:%511=345%:%

@@

%:%533=383%:%

@@

%:%535=385%:%
%:%537=387%:%
%:%538=387%:%
%:%539=388%:%
%:%540=389%:%
%:%542=390%:%
%:%543=390%:%
%:%544=391%:%
%:%546=392%:%
%:%547=392%:%
%:%548=393%:%

@@

%:%552=396%:%
%:%553=397%:%
%:%554=398%:%
%:%555=398%:%
%:%556=399%:%

@@

%:%562=404%:%
%:%563=405%:%
%:%564=406%:%
%:%565=406%:%
%:%566=407%:%
%:%568=408%:%
%:%569=409%:%
%:%570=409%:%
%:%571=410%:%
%:%574=411%:%
%:%578=411%:%
%:%579=411%:%
%:%580=411%:%
%:%582=412%:%
%:%583=413%:%
%:%584=414%:%

@@

%:%595=417%:%

@@

%:%597=419%:%
%:%599=421%:%
%:%600=421%:%
%:%601=422%:%
%:%603=423%:%
%:%604=423%:%
%:%605=424%:%
%:%607=425%:%
%:%608=425%:%
%:%609=426%:%
%:%611=427%:%
%:%612=427%:%
%:%613=428%:%
%:%615=429%:%
%:%616=429%:%
%:%617=430%:%
%:%619=431%:%
%:%620=432%:%
%:%621=432%:%
%:%622=433%:%
%:%629=434%:%
%:%630=434%:%
%:%631=435%:%
%:%632=435%:%
%:%633=436%:%
%:%634=436%:%
%:%635=436%:%
%:%636=437%:%
%:%637=437%:%
%:%638=438%:%
%:%639=438%:%
%:%640=438%:%
%:%641=439%:%
%:%642=439%:%
%:%643=440%:%
%:%644=440%:%
%:%645=440%:%
%:%646=441%:%

@@

%:%689=476%:%
%:%690=477%:%
%:%691=478%:%
